Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-07-08 paper/outro.tex
edits
Add the image back for the tool, add a reference to PwT-C11 in Conclusion

This paper is the first to present a direct denotational semantics for
sequential composition in a relaxed memory model which can be
efficiently compiled to modern CPUs. There is, as usual, more research
to be done.

@@

We've also not handled access elimination: store-forwarding and
dead-write-removal are unsound.  We expect that these can be validated by
allowing events with different labels to merge in some instances.

>>>>

This paper is the first to present a direct denotational semantics for
sequential composition in a relaxed memory model which can be
efficiently compiled to modern CPUs. We extract from this model a semantic dependency relation and use it to build \PwTc, a solution to the Out-of-Thin-Air problem in \cXI. There is, as usual,
more research to be done.

@@

\PwTmca{} does not validate access elimination: store-forwarding and
dead-write-removal are unsound.  We expect that these can be validated by
allowing events with different labels to merge in some instances.
